WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2021-01-03 lit/sec_1-fews.tex
Fixed: Removed NWMs abbreviation

Deltares developed \acrshort{fews} \cite{Werner2013TheSystem} in Netherland for operational forecasting agencies. The \acrshort{fews} codebase is not fully open source at the moment. The main objective of a forecasting system is to run multiple NWMs, hydrologic models, and hydrodynamic models which are required for the predictions. This approach is known as a model-centric approach \cite{Werner2005FloodCatchments}. In the model-centric approach, the inputs need to be in the format specific to the model. Also, the outputs produced by the models are specific to the model; hence, difficult to integrate with other models. For example, FLO2D creates human-readable text files as output. However, the Delft-FEWS uses a more modular approach, which is easier to integrate new models and update the system for new requirements. Thus, Delft-FEWS is an integration framework or middleware for the models, rather specific model workflow for weather forecasting.

>>>>

Deltares developed \acrshort{fews} \cite{Werner2013TheSystem} in Netherland for operational forecasting agencies. The \acrshort{fews} codebase is not fully open source at the moment. The main objective of a forecasting system is to run multiple \acrshort{nwm}s, hydrologic models, and hydrodynamic models which are required for the predictions. This approach is known as a model-centric approach \cite{Werner2005FloodCatchments}. In the model-centric approach, the inputs need to be in the format specific to the model. Also, the outputs produced by the models are specific to the model; hence, difficult to integrate with other models. For example, FLO2D creates human-readable text files as output. However, the Delft-FEWS uses a more modular approach, which is easier to integrate new models and update the system for new requirements. Thus, Delft-FEWS is an integration framework or middleware for the models, rather specific model workflow for weather forecasting.

### 2021-01-03 results/sec_1-test_plan.tex
Fixed: Removed NWMs abbreviation

The percentage of number of requests per each data type that comes to the system at a given time can be varied depending on the situation. The majority of weather data requests come from weather stations and other observation tools. Then we need to validate and modify those timeseries data and store them as new timeseries that can directly feed into the NWMs. These weather stations can send the weather data at different frequencies with different parameters such as precipitation, temperature, humidity, and wind direction. Most of the timeseries mentioned above are scalar timeseries. When compared to scalar data, parameters such as wind direction are vector timeseries with a lesser percentage of requests. Alternatively, most of the grid type data was generated as results of NWMs. But those grid data produce in less frequency due to the cost of the computer resource to produce results. After considering those factors we came up with 70\% scalar, 20\% vector, and 10\% grid percentage values as the expected requests rate ratios.
As an upper limit of such scenarios while designing the performance testing, it uses the following;
\begin{itemize}
    \item Hourly (24 data points)
    \item Every 30 minutes (48 data points)
    \item Every 15 minutes (96 data points) - One request is equivalent to a set of data points sent by a weather station in 15-minute interval for a single day
\end{itemize}

>>>>

The percentage of number of requests per each data type that comes to the system at a given time can be varied depending on the situation. The majority of weather data requests come from weather stations and other observation tools. Then we need to validate and modify those timeseries data and store them as new timeseries that can directly feed into the \acrshort{nwm}s. These weather stations can send the weather data at different frequencies with different parameters such as precipitation, temperature, humidity, and wind direction. Most of the timeseries mentioned above are scalar timeseries. When compared to scalar data, parameters such as wind direction are vector timeseries with a lesser percentage of requests. Alternatively, most of the grid type data was generated as results of \acrshort{nwm}s. But those grid data produce in less frequency due to the cost of the computer resource to produce results. After considering those factors we came up with 70\% scalar, 20\% vector, and 10\% grid percentage values as the expected requests rate ratios.
As an upper limit of such scenarios while designing the performance testing, it uses the following;
\begin{itemize}
    \item Hourly (24 data points)
    \item Every 30 minutes (48 data points)
    \item Every 15 minutes (96 data points) - One request is equivalent to a set of data points sent by a weather station in 15-minute interval for a single day
\end{itemize}
